% Created 2018-04-20 Fri 17:37
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage{amsmath}
\usepackage{paralist}
\usepackage[utf8]{inputenc}
\usepackage{palatino}
\usepackage{euler}
\usepackage{setspace}
\renewcommand{\em}[1]{\textbf{#1}}
\newcommand{\E}[1]{\operatorname{\mathbb{E}}[#1]}
\setstretch{1.1}
\let\itemize\compactitem
\let\description\compactdesc
\let\enumerate\compactenum
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
\newcommand{\RR}{\mathbb{R}}
\author{Bart Frenk}
\date{\today}
\title{Notes on hash kernels}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 25.1.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle

\section{Meta}
\label{sec-1}


\begin{enumerate}
\item Weinberger, Dasgupta, Langford, Smola, Attenberg. Feature hashing for large
scale multitask learning. Proceedings of the 26th International Conference on
Machine Learning, Montreal, Canada, 2009. (Mostly Yahoo!)
\item Shi, Petterson, Langford, Smola, Strehl, Dror, Vishnwanathan. Hash
kernels. 2009.
\end{enumerate}

\section{Feature hashing for large scale multitask learning}
\label{sec-2}

Use a random function to map a higher dimensional space (of features) into a
lower dimensional space. The expectation of the inner product of the range
equals the inner product on the domain.

The article is sloppy with probability distributions. How to define one on the
function space $\{1, \ldots, m\} \rightarrow \mathbb{R}$?.

\subsection{Introduction}
\label{sec-2-1}
\subsection{Hash functions}
\label{sec-2-2}

Let $\mathcal{X}$ be a high dimensional feature space, and $\mathcal{Y}$ a lower
dimensional target space. Both are equipped with inner products. The aim is to
define a random variable $\Phi$ with values in the function space $\mathcal{X}
\rightarrow \mathcal{Y}$, such that
\[
x_1 \cdot x_2 = \mathbb{E}(\Phi(x_1) \cdot \Phi(x_2)).
\]
It is important that $\Phi(x_1) \cdot \Phi(x_2)$ has low variance.




\section{Hash kernels}
\label{sec-3}

\section{Experiments}
\label{sec-4}
% Emacs 25.1.1 (Org mode 8.2.10)
\end{document}